Title

### 2019-05-22 4_method.tex
move beading strategy to before MAT section

@@

\subsection{Beading strategy}
The next step is to determine how we will fill a given distance between the outline and a significant/marked MAT segment with a whole number of beads. We want to fit an exact whole number of beads in order to prevent a gap being generated.

>>>>

\subsection{Beading strategy}
First we determine how we should fill a 	polygon with constant width with a number of beads.
We want to fit an exact whole number of beads in order to prevent a gap being generated.
We consider only half of the polygon, because our beading strategy should be symmetrical.

\subsection{Medial Axis}
In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
There are several possible skeletonal structures we could consider.

@@
